---
title: "GolfBall_HypothesisTest"
author: "Abhishek Kishore"
date: "25/06/2020"
output: github_document
---

## Objective
The Par Inc. wants to compare the driving distances between the new golf balls (new longer lasting balls with cut-resistance coating) and current balls. To do this comparision, 40 balls of both the new and current models were subjected to distance tests. The testing was performed with a mechanical hitting machine so that any difference between the mean distances for the two models could be attributed to a difference in the design.

## Assumptions

Following assumptions had been made for driving the insights:
•	The sample size is 40 (>30). Hence as per Centeral Limit Theorem, the sampling distribution of the mean will approach a normal distribution as the size of the sample increases and becomes large (>30). So it can be assumed, Population distribution is normal.
•	Observations are independent.
•	Population standard deviation or the variance is same in both samples.
•	Level of significance (α) = 0.05, as no specific level of significance has been provided.

```{r echo=FALSE}
rm(list = ls())

setwd("./Data")

library(xlsx)

golf = read.xlsx("golf.xls",sheetName = "Data")

attach(golf)
```
 
## Exploratory Data Analysis

```{r}
str(golf)
```

Following had been observed for the provided data:
•	Number of observations: 40
•	Number of variables: 2 
•	Names of the variable: Current & New
•	Current: This variable provides the observations for current golf balls.
•	New: This variable provides the observations for the new golf ball with coating designed to resist cuts.

# Missing values
```{r}
sum(is.na(golf))
```

